---
title: ""
output:
  rmarkdown::html_document:
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(ggmap)
library(ggplot2)
library(leaflet)
library(readxl)
library(dplyr)
library(stringr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(janitor)

```


### Falmouth Litter Reduction Team Survey Efforts

```{r, echo = F, warning = F, out.width = "100%", fig.height = 7}
data.dir <- here::here("data")
load(file = file.path(data.dir,"flrt_data.rdata"))

falmouth <- c(-70.693531,41.53, -70.448287,  41.625940)


leaflet() %>%
  setView(lng = -70.617672, lat = 41.564279, zoom = 12) %>%
  addTiles() %>% 
  addPolylines(data = flrt_nonrandom_surv1, color = "black", 
               popup = ~paste("Nips found:", as.character(count))) %>% 
  addPolylines(data = flrt_random_surv, color = "red") 


```

Collection sites for FLRT roadside litter surveys. Paths shown in red are related to a project specifically concerned with nip abundance on Falmouth roads. Black lines show general litter collection efforts where nips were also counted. **Click on black lines** to return the number of nips found in that survey effort.  